NN_Accel_Heading

### 2024-03-06 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before unchunking so early

fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
                                              Fish3_X = Fish1_X,
                                              Fish3_Y = Fish1_Y,
                                              Fish3_Z = Fish1_Z,
                                              Fish3_Speed = Fish1_Speed,
                                              Fish3_Accel = Fish1_Accel,
                                              Fish3_Yaw_Heading = Fish1_Yaw_Heading,
                                              Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
                                              ) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_X = Fish2_X,
                                              Fish1_Y = Fish2_Y,
                                              Fish1_Z = Fish2_Z,
                                              Fish1_Speed = Fish2_Speed,
                                              Fish1_Accel = Fish2_Accel,
                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading,
                                              Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_X = Fish3_X,
                                              Fish2_Y = Fish3_Y,
                                              Fish2_Z = Fish3_Z,
                                              Fish2_Speed = Fish3_Speed,
                                              Fish2_Accel = Fish3_Accel,
                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading,
                                              Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
                                       #Switch around angle when we switch focal fish
                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180)) %>%
                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))

@@

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Angle_Rads = deg2rad(Angle),
                                           RelativeX = Fish1_X - Fish2_X,
                                           RelativeY = Fish1_Y - Fish2_Y,
                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))

@@

nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Distance,0.5)) %>%
                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
accel_lin_lm <- lm(Fish1_Accel ~ Distance*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))

@@

ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Distance, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_smooth(se = F, method = glm, formula = y ~ x)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  ylim(-0.01, 0.01) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")

ggplot(nn_accel_sum %>% filter(Flow == "Still Water" & distance_bins < 3),
       aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ x)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")

>>>>

fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
                                              Fish3_X = Fish1_X,
                                              Fish3_Y = Fish1_Y,
                                              Fish3_Z = Fish1_Z,
                                              Fish3_Speed = Fish1_Speed,
                                              Fish3_Accel = Fish1_Accel,
                                              Fish3_Yaw_Heading = Fish1_Yaw_Heading,
                                              Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
                                              ) %>%
                                       mutate(Fish1 = Fish2,
                                              Fish1_X = Fish2_X,
                                              Fish1_Y = Fish2_Y,
                                              Fish1_Z = Fish2_Z,
                                              Fish1_Speed = Fish2_Speed,
                                              Fish1_Accel = Fish2_Accel,
                                              Fish1_Yaw_Heading = Fish2_Yaw_Heading,
                                              Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
                                       mutate(Fish2 = Fish3,
                                              Fish2_X = Fish3_X,
                                              Fish2_Y = Fish3_Y,
                                              Fish2_Z = Fish3_Z,
                                              Fish2_Speed = Fish3_Speed,
                                              Fish2_Accel = Fish3_Accel,
                                              Fish2_Yaw_Heading = Fish3_Yaw_Heading,
                                              Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
                                       #Switch around angle when we switch focal fish
                                       mutate(Angle = ifelse(Angle < 0, Angle + 180, Angle - 180),
                                              Relative_X = -1*Relative_X) %>%
                                       select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))

@@

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Angle_Rads = deg2rad(Angle),
                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))

@@

nn_accel_sum <- fish_data_nn %>% mutate(distance_bins = round_any(Relative_X,0.25)) %>%
                                                group_by(distance_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_accel = mean(Fish1_Accel, na.rm = T),
                                                          sd_accel = sd(Fish1_Accel, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

accel_base_lm <- lm(Fish1_Accel ~ Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))
accel_lin_lm <- lm(Fish1_Accel ~ Relative_X*Flow_Ablation_Darkness, data = fish_data_nn %>% filter(Flow == "Still Water"))

@@

ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Relative_X, y = Fish1_Accel, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_smooth(se = F, method = glm, formula = y ~ x)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  #ylim(-0.01, 0.01) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")

ggplot(nn_accel_sum %>% filter(Flow == "Still Water" & distance_bins < 3),
       aes(x = distance_bins, y = mean_accel, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.75) +
  geom_smooth(se = F, method = glm, formula = y ~ 1)+
  theme_classic() +
  xlab("distance from neighbour (BL)") +
  ylab("focal fish acceleration (BL/s^2)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  labs(color = "Sensory Conditions")
